Figures

### 2019-09-03 figures/07_model-selection.Rmd
cleanup labels

```{r tp_fe, out.width="3.25in", out.height="4in"}
# lapply(re_brms, function(x) x $formula) 
# re_brms[[6]]$formula
best_tp        <- 6 # 6 is best tp model with random effects
fit_tp         <- re_brms[[best_tp]] 
signif_hu4_ids <- fit_tp$re_signif_ids 
signif_hu4     <- dplyr::filter(hu4, ZoneID %in% signif_hu4_ids)

@@

gg_tp <- spread_draws(fit_tp, `b_.*`, regex = TRUE) %>%
  tidyr::gather(key = "key", value = "value", -.chain, -.iteration, -.draw) %>%
  dplyr::filter(key != "b_Intercept") %>%
  mutate(key = stringr::str_replace(key, "b_", "")) %>%
  left_join(pred_key, by = c("key" = "varv")) %>%
  group_by(pretty) %>%
  summarize(value = list(tibble::enframe(
    quantile(value, probs=c(0.05,0.5,0.95))))) %>% unnest() %>%
  tidyr::spread(name, value) %>%
  dplyr::bind_rows(
    dplyr::select(re_global[best_tp,], -term, -response)) %>%
  rowwise() %>%
  mutate(signif = (`5%` > 0 & `95%` > 0)| (`5%` < 0 & `95%` < 0)) %>%
  left_join(dplyr::select(pred_key, pretty, category)) %>%
  mutate(category = factor(category, 
                           levels = rev(c("Nutrient inputs", "Nutrient transport", 
                                      "Buffer configuration", "Lake", 
                                      "Land-use cover")))) %>%
  mutate(category = forcats::fct_recode(category, 
                                        Buffer = "Buffer configuration")) %>%
  arrange(category) %>%
  ungroup() %>% mutate(pretty = factor(pretty, levels = pretty)) %>%
  arrange(category, pretty)

gg_tp_fe <- 
  ggplot(data = gg_tp) + 
  geom_pointrange(aes(x = pretty, y = `50%`, 
                      ymin = `5%`, ymax = `95%`, color = signif)) + 
  expand_limits(y = -1.8) +
  geom_rect(ymin = -0.6, ymax = -0.6 - 2, xmin = 0, xmax = nrow(gg_tp) + 1, 
              fill = "transparent") +
  geom_text(aes(x = pretty, label = pretty, color = signif), 
            y = -0.65, vjust = 0.5, hjust = "right") + 
  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
  geom_hline(yintercept = 0) +
  scale_y_continuous(breaks = seq(from = -0.6, to  = 0.4, by = 0.2), 
                     labels = scales::number_format(accuracy = 0.1)) +
  coord_flip() +
  theme(axis.text.y = element_blank(), 
        axis.ticks.y = element_blank(), 
        axis.title.y = element_blank()) + 
    facet_wrap(~category, strip.position = "left", ncol = 1, scales = "free_y",
               as.table = FALSE) +
    theme(panel.spacing = unit(0, "lines"), 
          strip.placement = "outside", 
          strip.background = element_blank(), 
          axis.title.y = element_blank()) + 
        ylab("Standardized slope") + theme(legend.position = 0) + 
        ggtitle("TP") + xlab("") +
  theme(panel.background = element_rect(fill = "transparent", color = NA),
        plot.background = element_rect(fill = "transparent", color = NA), 
        panel.grid = element_blank(),
        rect = element_rect(fill = "transparent"), 
        plot.title = element_text(hjust = 0.5, face = "bold")) + 
    annotate(x=0, xend=0, y=-0.6, yend=0.4, 
             colour="black", lwd=0.9, geom="segment") 
```

@@

```{r tn_fe, out.width="3.25in", out.height="4in"}
# lapply(re_brms, function(x) x$formula) 
# re_brms[[11]]$formula
best_tn        <- 11 # 11 is best tn model with random effects
fit_tn         <- re_brms[[best_tn]] 
signif_hu4_ids <- fit_tn$re_signif_ids 
signif_hu4     <- dplyr::filter(hu4, ZoneID %in% signif_hu4_ids)

# plot tn model fixed effects summary
# summary(fit_tn)
gg_tn <- spread_draws(fit_tn, `b_.*`, regex = TRUE) %>%
  tidyr::gather(key = "key", value = "value", -.chain, -.iteration, -.draw) %>%
  dplyr::filter(key != "b_Intercept") %>%
  mutate(key = stringr::str_replace(key, "b_", "")) %>%
  left_join(pred_key, by = c("key" = "varv")) %>%
  group_by(pretty) %>%
  summarize(value = list(tibble::enframe(
    quantile(value, probs=c(0.05,0.5,0.95))))) %>% unnest() %>%
  tidyr::spread(name, value) %>%
  dplyr::bind_rows(
    dplyr::select(re_global[best_tn,], -term, -response)) %>%
  rowwise() %>%
  mutate(signif = (`5%` > 0 & `95%` > 0)| (`5%` < 0 & `95%` < 0)) %>%
  left_join(dplyr::select(pred_key, pretty, category)) %>%
  mutate(category = factor(category, 
                           levels = rev(c("Nutrient inputs", "Nutrient transport", 
                                      "Buffer configuration", "Lake", 
                                      "Land-use cover")))) %>%
  mutate(category = forcats::fct_recode(category, 
                                        Buffer = "Buffer configuration")) %>%
  arrange(category) %>%
  ungroup() %>% mutate(pretty = factor(pretty, levels = pretty)) %>%
  arrange(category, pretty)

gg_tn_fe <- 
  ggplot(data = gg_tn) + 
  geom_pointrange(aes(x = pretty, y = `50%`, 
                      ymin = `5%`, ymax = `95%`, color = signif)) + 
  expand_limits(y = c(-0.6, 1.6)) +
  geom_rect(ymin = 0.44, ymax = 0.44 + 2, xmin = 0, xmax = nrow(gg_tn) + 1, 
              fill = "transparent") +
  geom_text(aes(x = pretty, label = pretty, color = signif), 
            y = 0.44, vjust = 0.5, hjust = "left") + 
  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
    geom_hline(yintercept = 0) +
  scale_y_continuous(breaks = seq(from = -0.6, to  = 0.4, by = 0.2), 
                     labels = scales::number_format(accuracy = 0.1)) +
  coord_flip() +
  theme(axis.text.y = element_blank(), 
        axis.ticks.y = element_blank(), 
        axis.title.y = element_blank()) + 
    facet_wrap(~category, strip.position = "right", ncol = 1, scales = "free_y",
               as.table = FALSE) +
    theme(panel.spacing = unit(0, "lines"), 
          strip.placement = "outside", 
          strip.background = element_blank(), 
          axis.title.y = element_blank()) + 
        ylab("Standardized slope") + theme(legend.position = 0) + 
        ggtitle("TN") + xlab("") +
  theme(panel.background = element_rect(fill = "transparent"), 
        panel.grid = element_blank(),
        rect = element_rect(fill = "transparent"), 
        plot.title = element_text(hjust = 0.5, face = "bold")) + 
    annotate(x=0, xend=0, y=-0.6, yend=0.4, 
             colour="black", lwd=0.9, geom="segment")

>>>>

```{r tp_fe, out.width="3.45in", out.height="4in"}
# lapply(re_brms, function(x) x $formula) 
# re_brms[[6]]$formula
best_tp        <- 6 # 6 is best tp model with random effects
fit_tp         <- re_brms[[best_tp]] 
signif_hu4_ids <- fit_tp$re_signif_ids 
signif_hu4     <- dplyr::filter(hu4, ZoneID %in% signif_hu4_ids)

@@

gg_tp <- spread_draws(fit_tp, `b_.*`, regex = TRUE) %>%
  tidyr::gather(key = "key", value = "value", -.chain, -.iteration, -.draw) %>%
  dplyr::filter(key != "b_Intercept") %>%
  mutate(key = stringr::str_replace(key, "b_", "")) %>%
  left_join(pred_key, by = c("key" = "varv")) %>%
  group_by(pretty) %>%
  summarize(value = list(tibble::enframe(
    quantile(value, probs=c(0.05,0.5,0.95))))) %>% unnest() %>%
  tidyr::spread(name, value) %>%
  dplyr::bind_rows(
    dplyr::select(re_global[best_tp,], -term, -response), 
    data.frame(pretty = "", `5%` = "", `50%` = "", `95%` = "", 
               stringsAsFactors = FALSE)
    ) %>%
  rowwise() %>%
  mutate(signif = (`5%` > 0 & `95%` > 0)| (`5%` < 0 & `95%` < 0)) %>%
  left_join(dplyr::select(pred_key, pretty, category)) %>%
  mutate(category = tidyr::replace_na(category, "Land-use cover")) %>%
  mutate(category = factor(category, 
                           levels = rev(c("Nutrient inputs", "Nutrient transport", 
                                      "Buffer configuration", "Lake", 
                                      "Land-use cover")))) %>%
  mutate(category = forcats::fct_recode(category, 
                                        Buffer = "Buffer configuration", 
                                        LULC = "Land-use cover")) %>%
  arrange(category) %>%
  ungroup() %>% mutate(pretty = factor(pretty, levels = pretty)) %>%
  arrange(category, pretty)

gg_tp_fe <- 
  ggplot(data = gg_tp) + 
  geom_pointrange(aes(x = pretty, y = `50%`, 
                      ymin = `5%`, ymax = `95%`, color = signif)) + 
  expand_limits(y = -1.8) +
  geom_rect(ymin = -0.6, ymax = -0.6 - 2, xmin = 0, xmax = nrow(gg_tp) + 1, 
              fill = "transparent") +
  # y-axis labels
  geom_text(aes(x = pretty, label = pretty, color = signif), 
            y = -0.65, vjust = 0.5, hjust = "right") + 
  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
  geom_hline(yintercept = 0) +
  # x-axis labels
  scale_y_continuous(breaks = seq(from = -0.6, to  = 0.6, by = 0.2), 
                     labels = scales::number_format(accuracy = 0.1)) +
  coord_flip() +
  theme(axis.text.y = element_blank(), 
        axis.ticks.y = element_blank(), 
        axis.title.y = element_blank()) + 
    facet_wrap(~category, strip.position = "left", ncol = 1, scales = "free_y",
               as.table = FALSE) +
    theme(panel.spacing = unit(0, "lines"), 
          strip.placement = "outside", 
          strip.background = element_blank(), 
          axis.title.y = element_blank()) + 
        ylab("Standardized slope") + theme(legend.position = 0) + 
        ggtitle("TP") + xlab("") +
  theme(panel.background = element_rect(fill = "transparent", color = NA),
        plot.background = element_rect(fill = "transparent", color = NA), 
        panel.grid = element_blank(),
        rect = element_rect(fill = "transparent"), 
        plot.title = element_text(hjust = 0.5, face = "bold")) + 
    # x-axis line length; controls dot-plot extent
    annotate(x=0, xend=0, y=-0.6, yend=0.6, 
             colour="black", lwd=0.9, geom="segment") 
```

@@

```{r tn_fe, out.width="3.45in", out.height="4in"}
# lapply(re_brms, function(x) x$formula) 
# re_brms[[11]]$formula
best_tn        <- 11 # 11 is best tn model with random effects
fit_tn         <- re_brms[[best_tn]] 
signif_hu4_ids <- fit_tn$re_signif_ids 
signif_hu4     <- dplyr::filter(hu4, ZoneID %in% signif_hu4_ids)

# plot tn model fixed effects summary
# summary(fit_tn)
gg_tn <- spread_draws(fit_tn, `b_.*`, regex = TRUE) %>%
  tidyr::gather(key = "key", value = "value", -.chain, -.iteration, -.draw) %>%
  dplyr::filter(key != "b_Intercept") %>%
  mutate(key = stringr::str_replace(key, "b_", "")) %>%
  left_join(pred_key, by = c("key" = "varv")) %>%
  group_by(pretty) %>%
  summarize(value = list(tibble::enframe(
    quantile(value, probs=c(0.05,0.5,0.95))))) %>% unnest() %>%
  tidyr::spread(name, value) %>%
  dplyr::bind_rows(
    dplyr::select(re_global[best_tn,], -term, -response), 
    data.frame(pretty = "", `5%` = "", `50%` = "", `95%` = "", 
               stringsAsFactors = FALSE)
    ) %>%
  rowwise() %>%
  mutate(signif = (`5%` > 0 & `95%` > 0)| (`5%` < 0 & `95%` < 0)) %>%
  left_join(dplyr::select(pred_key, pretty, category)) %>%
  mutate(category = tidyr::replace_na(category, "Land-use cover")) %>%
  mutate(category = factor(category, 
                           levels = rev(c("Nutrient inputs", "Nutrient transport", 
                                      "Buffer configuration", "Lake", 
                                      "Land-use cover")))) %>%
  mutate(category = forcats::fct_recode(category, 
                                        Buffer = "Buffer configuration", 
                                        LULC = "Land-use cover")) %>%
  arrange(category) %>%
  ungroup() %>% mutate(pretty = factor(pretty, levels = pretty)) %>%
  arrange(category, pretty)

gg_tn_fe <- 
  ggplot(data = gg_tn) + 
  geom_pointrange(aes(x = pretty, y = `50%`, 
                      ymin = `5%`, ymax = `95%`, color = signif)) + 
  expand_limits(y = c(-0.6, 1.6)) +
  geom_rect(ymin = 0.44, ymax = 0.44 + 2, xmin = 0, xmax = nrow(gg_tn) + 1, 
              fill = "transparent") +
  geom_text(aes(x = pretty, label = pretty, color = signif), 
            y = 0.65, vjust = 0.5, hjust = "left") + 
  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
    geom_hline(yintercept = 0) +
  scale_y_continuous(breaks = seq(from = -0.6, to = 0.6, by = 0.2), 
                     labels = scales::number_format(accuracy = 0.1)) +
  coord_flip() +
  theme(axis.text.y = element_blank(), 
        axis.ticks.y = element_blank(), 
        axis.title.y = element_blank()) + 
    facet_wrap(~category, strip.position = "right", ncol = 1, scales = "free_y",
               as.table = FALSE) +
    theme(panel.spacing = unit(0, "lines"), 
          strip.placement = "outside", 
          strip.background = element_blank(), 
          axis.title.y = element_blank()) + 
        ylab("Standardized slope") + theme(legend.position = 0) + 
        ggtitle("TN") + xlab("") +
  theme(panel.background = element_rect(fill = "transparent"), 
        panel.grid = element_blank(),
        rect = element_rect(fill = "transparent"), 
        plot.title = element_text(hjust = 0.5, face = "bold")) + 
    annotate(x=0, xend=0, y=-0.6, yend=0.6, 
             colour="black", lwd=0.9, geom="segment")
